\makepositions{

    \position{Office Manager \& Volunteer}{}
    {Zhanjiang, Guangdong, China}
    {BlueRibbon Ocean Conservation Association in Guangdong Ocean University}
    {Oct 2019}{June 2020}
    {
        \item Strategically planned and led the Longhaitian Beach cleanup initiative in Zhanjiang, enhancing community engagement and environmental conservation efforts.
\item Facilitated effective coordination and communication across multiple departments to ensure smooth operational workflow.
\item Compiled and produced the comprehensive annual report highlighting key organizational milestones and events.
\item Oversaw the organization and maintenance of all office documentation and records.
    }
    \position{Co-Founder \& Advisor}{}
    {Zhanjiang, Guangdong, China}
    {Xinyuntian Meteorological and Oceanographic Technology Studio}
    {Jan 2020}{June 2021}
    {
        \item Co-established the studio leveraging the “Xinyuntian Weather” WeChat public platform, based at Guangdong Ocean University.
        \item Coordinated resources and collaborations among multiple universities including Nanjing University of Information Science \& Technology, Ocean University of China, and Lanzhou University.
        \item Provided comprehensive services to the meteorological industry such as new media information dissemination, conference and exhibition organization, talent exchange, and international publishing support.
    }
    \position{Deputy Liaison Officer}{}
    {Qingdao, Shandong, China}
    {Deputy Liaison Officer for Joint Training Graduate Students (Class of 2021)}
    {Sep 2022}{Jun 2024}
    {
        \item Managed the collection, organization, and dispatch of academic materials for proposal, mid-term, and graduation defenses of joint training graduate students between FIO and HEU.
        \item Coordinated communication and party/youth league relations between the School and the Qingdao Innovation Development Base during the principal liaison officer’s absence.
    }

   
}
