\makeprojects{
    \project{Library Management System}
    {C++, Multithreading, Networking, Persistence, Catch2, CMake, Doxygen}
    {October 2024}{January 2025}
    {https://github.com/alfieatkinson/library-management-system}
    {
        \item \textbf{Developed a console-based library management system} in C++ with CRUD operations for books, users, and transactions, leveraging Object-Oriented Programming principles.
        \item \textbf{Implemented multithreading capabilities} to support concurrent user operations, optimising system performance under load.
        \item \textbf{Designed and integrated networking capabilities} to allow remote interactions, laying the groundwork for distributed library management.
        \item \textbf{Incorporated data persistence mechanisms} to enable reliable storage and retrieval of library data across sessions.
        \item \textbf{Built a modular directory structure} with clear separation of concerns, using CMake for build automation and Doxygen for automated documentation generation.
        \item \textbf{Adopted Test-Driven Development (TDD)} with Catch2 to ensure robust and reliable code through comprehensive unit testing.
    }

    \project{Dissertation Project: Sentiment Analysis Tool}
    {Python, TensorFlow, Keras, PyQt6, Machine Learning}
    {September 2023}{May 2024}
    {https://github.com/alfieatkinson/sentiment-analysis-tool}
    {
        \item \textbf{Implemented and fine-tuned deep learning models} for sentiment classification, utilising TensorFlow and Keras to achieve high accuracy and robustness in detecting sentiment from diverse textual data.
        \item \textbf{Optimised data pipelines} to handle and pre-process large volumes of social media data efficiently, enabling real-time sentiment analysis and reducing processing time by 30\%.
        \item \textbf{Designed and deployed an interactive GUI using PyQt6,} allowing users to easily visualise sentiment trends, track brand sentiment over time, and customise search terms and settings for tailored insights.
        \item \textbf{Conducted comprehensive testing and validation} to ensure the accuracy and reliability of the sentiment analysis tool, including cross-validation of models and user feedback sessions.
    }
}